---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/R/R - Datascripts/Assignment 5")
#Load library
library(ggplot2);library(pastecs);library(rmarkdown);library(tidyr);
library(dplyr);library(QuantPsyc);library(VIF);library(stringr);library(tidytext);library(DHARMa)
library(lme4);library(lmerTest);library(psych);library(MuMIn);library(tidyverse);library(magrittr);library(Metrics);library(caret);library(readtext);library(readr)


library(crqa);library(plyr);library(Matrix);library(tseriesChaos);library(deSolve);library(fields);library(spam);library(grid)


files = read.delim("Data.csv", header = TRUE, sep =";")
```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 
```{r}
library(metafor)
#install.packages("metafor", dependencies = T)


sum(files$SampleSizeSchizo)
#518 Schitzophrenic participants
mean(files$SampleSizeSchizo)
#37


sum(files$SampleSizeContros, na.rm = T)
#216 Control participants
mean(files$SampleSizeContros, na.rm = T)
#24

#734 overall across studies.


#Control
table(files$PitchMeanControls, exclude=NULL) 
#4 reported, 10 didn't
table(files$PitchMeanControlsSD, exclude=NULL) 
#4 studies reported this, 10 didnt
table(files$PitchSDControls, exclude=NULL)
#6 reported, 8 didn't
table(files$PitchSDControlsSD, exclude=NULL)
#6 reported, 8 didn't

#Schitzo
table(files$PitchMeanSchizo, exclude=NULL) 
#4 reported, 10 didn't 
table(files$PitchMeanSchizoSD, exclude=NULL) 
#4 reported, 10 didn't
table(files$PitchSDSchizo, exclude=NULL)
#11 reported, 3 didn't
table(files$PitchSDSchizoSD, exclude=NULL)
#11 reported, 3 didn't

#N1i = sample size schi
#N12 = sample size control
#m1i = mean size schi
#m2i = mean size control
#sd1i = mean SD schi
#sd2i = mean SD control

#Mean
PitchMean= escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchMeanControls, m2i=PitchMeanSchizo, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = files)

#Rma model. Slab means random effect, we control for different methods for the articles.
#yi = effectsize, vi = SD^2
rma1 = rma(yi, vi, data = PitchMean, slab = Article)

#Forrest plot
rmaPlotMean = forest(rma1)


#Lmer test
Model1 <- lmer(yi ~ 1 + (1|Article), weights = 1/vi, data=PitchMean, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))

#SD_________________________________________________________________________________

#SD
PitchSD = escalc('SMD', n1i= SampleSizeSchizo, n2i=SampleSizeContros, m1i= PitchSDControls, m2i= PitchSDSchizo, sd1i=PitchSDControlsSD, sd2i=PitchSDSchizoSD, data = files)

#RMA
rma2 = rma(yi, vi, data=PitchSD, slab=Article)

#Forest
rmaPlotSD = forest(rma2)

#Lmer test
Model2 <- lmer(yi ~ 1 + (1|Article), weights = 1/vi, data=PitchSD, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))



```


2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.
```{r}
#Load own data from assignment 3
A3_data <- read.delim("final_rqax.csv", header = TRUE, sep =",")

#For Control Mean
#Mean = 135.0317
mean(A3_data$mean[A3_data$diagnosis == "control"])
#SD = 47.7987
sd(A3_data$mean[A3_data$diagnosis=="control"])

#For Control SD
#Mean = 25.61366
mean(A3_data$stdDev[A3_data$diagnosis == "control"])
#SD = 17.90346
sd(A3_data$stdDev[A3_data$diagnosis=="control"])

#For Schi Mean
#Mean = 149.079
mean(A3_data$mean[A3_data$diagnosis == "schizophrenia"])
#SD = 57.83132
sd(A3_data$mean[A3_data$diagnosis=="schizophrenia"])

#For Schi SD
#Mean = 24.02952
mean(A3_data$stdDev[A3_data$diagnosis == "schizophrenia"])
#SD = 36.78883
sd(A3_data$stdDev[A3_data$diagnosis=="schizophrenia"])

#Find variables for A3
#Get controls
Samp_Con =length(unique(A3_data$participant[A3_data$diagnosis == "control"]))

Samp_Schi = length(unique(A3_data$participant[A3_data$diagnosis == "schizophrenia"]))

#Make df so i can bind my variables to the meta set.  
A3 <- data.frame("Article" = "BAMF", "Year" = "2017", "SampleSizeSchizo" = Samp_Schi, "SampleSizeContros" = Samp_Con, "PitchMeanControls" = 135.0317, "PitchMeanControlsSD" = 47.7987, "PitchMeanSchizo" = 149.079, "PitchMeanSchizoSD"= 57.83132, "PitchSDControls" =25.61366, "PitchSDControlsSD" = 17.90346, "PitchSDSchizo" = 24.02952, "PitchSDSchizoSD" = 36.78883)

#Bind by rows
Combo <- rbind(files, A3)

#New mean for participants
mean(Combo$SampleSizeSchizo)
#38.333
mean(Combo$SampleSizeContros, na.rm = T)
#27.5

#N1i = sample size schi
#N12 = sample size control
#m1i = mean size schi
#m2i = mean size control
#sd1i = mean SD schi
#sd2i = mean SD control

NEW_PitchMean= escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchMeanControls, m2i=PitchMeanSchizo, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = Combo)

#Rma model. Slab means random effect, we control for different methods for the articles.
#yi = effectsize, vi = SD^2
rmaComboMean = rma(yi, vi, data = NEW_PitchMean, slab = Article)

#Forrest plot
ComboMeanPlot = forest(rmaComboMean)

#SD
NEW_PitchSD = escalc('SMD', n1i= SampleSizeSchizo, n2i=SampleSizeContros, m1i= PitchSDControls, m2i= PitchSDSchizo, sd1i=PitchSDControlsSD, sd2i=PitchSDSchizoSD, data = Combo)

#RMA
rmaComboSD = rma(yi, vi, data=NEW_PitchSD, slab=Article)

#Forest
ComboSDPlot = forest(rmaComboSD)





```


3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.


```{r}
#Heterogeneity

#RMA Mean
rmaComboMean = rma(yi, vi, data = NEW_PitchMean, slab = Article)


#RMA SD
rmaComboSD = rma(yi, vi, data=NEW_PitchSD, slab=Article)

#Testing for influential studies
inf <- influence(rmaComboMean)
print(inf)
plot(inf)

inf2 <- influence(rmaComboSD)
print(inf2)
plot(inf2)

#Rank test
#Mean
ranktest(rmaComboMean)
#SD
ranktest(rmaComboSD)
#Funnel plot
#Mean
funnel(rmaComboMean, main = "Random-Effects Model",xlab = "Standardized Mean Difference")

#SD
funnel(rmaComboSD, main = "Random-Effects Model",xlab = "Standardized Mean Difference")

#Reg test
regtest(rmaComboMean)

regtest(rmaComboSD)



```



## Tips on the process to follow:

- Download the data on all published articles analyzing pitch in schizophrenia: https://www.dropbox.com/s/pmgw8wzc308so1p/Data.csv?dl=0
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))
 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

- Now look at the output of rma() and check tau and I2
